---
title: "Combine-climate-lite-scripts"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
abstract: This script combines all scripts previously run under CCRP's Climate Lite protocol for Resource Stewardship Strategies (RSS). 
---

NOTE: If you have trouble with packages loading from renv, go into your .Rprofile file and comment out the line ```source("renv/activate.R)```
Then restart R and re-run from your general package library (R will do this automatically upon restart if the above line is commented out). If you want to check what library R is accessing, type ```.libPaths()``` into your console. 

##

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  collapse = TRUE,
  warning = TRUE, # set to FALSE when done
  message = TRUE # set to FALSE when done
)

#renv::init() Only needs to be run 1x when project is initiated. No one should ever have to run this line again. 

#renv::restore() # This line will restore packages to the versions recorded in the lockfile. Collaborators can use this command to keep their packages current. This line should be run once a week.  

#renv::update(exclude = "WaterBalance") # This line should be run once a week by whoever is regularly using this script. The first time running this line, you might need to follow directions to create a Personal Access Token with GitHub. Simply follow directions printed in the console. If you run into trouble, contact Annie Kellner Dillon at anne_dillon@nps.gov 

# renv::snapshot() # This command takes a snapshot of the packages in their current state and records it in the lockfile. Renv will perform this task periodically. If a manual snapshot is desired, use this command to manually update the lockfile.   


library(here); library(plyr); # Use here::here when package lubridate is used
library(plotrix); library(zoo); library(ggplot2); library(grid); library(cowplot); library(reshape2); library(raster); library(ncdf4); library(reshape2); library(WriteXLS); library(data.table); library(RColorBrewer); library(ggrepel); library(lubridate); library(dplyr); library(forcats); library(openxlsx); library("WaterBalance"); library(sf); library(raster); library(rgdal); library(R.utils); library(tmap); library(tmaptools); library(rJava); library(OpenStreetMap); library(gridExtra); library(SPEI); library(tidyr); library(tibble); library(sp); library(skimr); library(cft)


```


There are two code chunks in which the RCF user should enter information that is park-specific. The first chunk contains inputs that are often changed (i.e., with each new park). The second chunk contains user inputs that are *rarely* changed (i.e., project lead has requested a change).

**First user input chunk (please enter park-specific information):**

```{r user-inputs-1}

rm(list = ls())


# --------------- Input local folder information ----------------------------- #

# When this document has finished running, the files will be copied to a local directory and all newly created files (e.g., figures) will be deleted from the repo

project_root_dir <- 'C:/Users/adillon/Documents/Repos/CCRP_Climate_Futures_v1.0' # local directory where your repo is stored
local_rss_dir <- 'C:/Users/adillon/Documents/RSS/CARE' # local directory where you want this repo copied. Should be something like 'C:/Users/adillon/Documents/RSS/CONG'

# -------------- Input site information -------------------------------------- #

SiteID = "CARE"
state <- "Utah"
Lat <- 38.383553
Lon <- -111.283004

# -------------- Inputs for NOAA ClimGrid Extraction --------------------------#



# -------------- Input information for Climate Futures analyses (MACA) ------- #

# Specify Climate Futures

FutureSubset <- c("Warm Wet","Hot Dry") # Pick pair of climate futures.
CFs<- c("Warm Wet", "Hot Dry") # Same as above

colors2<- c("#9A9EE5","#E10720")  # Select pair of climate futures - WarmWet/HotDry
#colors2<- c("#F3D3CB","#12045C")  # Select pair of climate futures - HotWet/WarmDry

# -------------- Input information for Water Balance model ------------------- #

WB_GCMs = c("MRI-CGCM3.rcp45","HadGEM2-ES365.rcp85") # Specific models need to be selected to run the Water Balance scripts

col<- c("darkgray","#9A9EE5","#E10720")  # WarmWet/HotDry
#col<- c("darkgray","#F3D3CB","#12045C")  # HotWet/WarmDry

```

**Second user input chunk (information that should only be changed when directly specified)**

```{r user-inputs-2}

CFs_all <- c("Warm Wet", "Hot Wet", "Central", "Warm Dry", "Hot Dry")

# ----------- Information for MACA parsing script ---- ----------------------- #

#Date ranges to be extracted

Future_StartYear = 2006   #2006-2099
Future_EndYear = 2099   #2006-2099
Hist_StartYear = 1950     #1950-2005
Hist_EndYear = 2005      #1950-2005

#Variable and scenario names corresponding to MACA data directory structure
vars = c("pr", "tasmax", "tasmin","rhsmax","rhsmin")
scens = c("rcp45", "rcp85")

#Variable names for output tables
VarNames = c("PrecipCustom", "TmaxCustom", "TminCustom","RHmaxCustom","RHminCustom")

# GCMs to be extracted
GCMs = c('bcc-csm1-1','bcc-csm1-1-m','BNU-ESM','CanESM2','CCSM4','CNRM-CM5','CSIRO-Mk3-6-0',
         'GFDL-ESM2G','GFDL-ESM2M','HadGEM2-CC365','HadGEM2-ES365',
         'inmcm4','IPSL-CM5A-MR','IPSL-CM5A-LR','IPSL-CM5B-LR',
         'MIROC5','MIROC-ESM','MIROC-ESM-CHEM','MRI-CGCM3','NorESM1-M')

Remove_files = "Y" # "N"       #Removes all climate data files saved in directory
                                # This code can also be changed for GridMet


# --------- Information for Climate Futures Analyses (MACA) ------------------ #

# Specify parameters:

Year = 2040 #Central year
Range = 30  #Number of years to summarize (should be at least 30)

# Threshold percentages for defining Climate futures. Default low/high:  0.25, 0.75
CFLow = 0.25     
CFHigh = 0.75

#Temperature/precip threshold values

HotTemp = 95    # deg F. Default should be about 100 deg F
ColdTemp = 32    # deg F
PrecipThreshold = 0.05    # inches per day. Precip Threshold (used to measure Drought duration). For many GCMs shoud not 
#  be 0 because models "drizzle". Some investigation necessary.
QuantileLow = 0.05   #Quantiles for temperature threshold calculations
QuantileHigh = 0.95

# -------------- Information for GridMET  ------------------------------------ #

var = c("pr","tmmx","tmmn")
longVar = c("precipitation_amount", "daily_maximum_temperature", "daily_minimum_temperature")
box = c(Lat+.5,Lat-.5,Lon+.5,Lon-.5)
startDate = "1979-01-01"
endDate = "2020-12-31"


# -------------- Information for Water Balance model ------------------- #

# The following needs to be inputted if the park centroid will not be used to select the MACA grid cell for the water balance model:

#MACA_lat <- 40.4465 
#MACA_lon <- -108.7651

# ------------ Information for drought analyses ------------------------ #

## SPEI variables

SPEI_per<-6 # This is the value for the period SPEI is aggregated. 6-months is standard but could change if want. 
truncation<- -.5 # SPEI value, under which drought events are considered
SPEI_start <- 1950
SPEI_end <- 1999

```


## Historical Trends

```{r PRISM-parse, eval = FALSE, message=FALSE, warning=FALSE, echo=FALSE}

#source(here::here("./PRISM/PRISM_4k_parse.R")) # Parses PRISM data. Output = "PARK_lat_long_PRISM_PptTminTmax_IntermediateFiles.RData" # NOTE: This script is excluded and has not been adapted to the new process

```

```{r Historical-trends-plots, results=hide, eval=TRUE} 

# Requires "PARK_lat_long_PRISM_PptTminTmax_IntermediateFiles.RData"
# Outputs plots into ./figures/Historical-trends
# If you get an error re: invalid 'description' argument, it means you did not upload the input data into the repo

#source(here::here("scripts", "Historical-trends", "RSS PRISM plots v1.2.R"),echo = FALSE) 

```


## Climate Futures (MACA)

```{r Climate-Futures, message=FALSE, warning=FALSE, include=FALSE, results=HIDE}

source(here::here("scripts", "Climate-Futures", "CFT_CF_parsing_v1.R")) # Parse MACA data. Output = "_init_parsed.RData". 

source(here::here("scripts", "Climate-Futures", "Gridmet-THREDD-download.R")) # Parse GridMET data. Output = "GridMet.csv"

source(here::here("scripts", "Climate-Futures", "RSS_MACA_Plot_Table_Creation.R"), local = knitr::knit_global()) # Requires "PARK_init_parsed.RData"; Output = "PARK_lat_long_Final_Environment.RData". 

source(here::here("scripts", "Climate-Futures", "RSS_MACA_Scatter and diagnostic.R"), local = knitr::knit_global()) # Creates scatter and diagnostic plots. Outputs to Figs MACA folder. 
```

```{r CF-plots}

if (exists("FutureSubset") == FALSE) stop("Please specify Climate Futures") # At the top of the script, please enter a combination of futures, e.g. Warm Wet/Hot Dry

source(here::here("scripts", "Climate-Futures", "RSS_Plotting_Bar_Charts.R")) # Requires "PARK_lat_long_Final_Environment.RData". Outputs plots and Excel Workbook 

```

# Water Balance

The get_params.R script extracts site parameters for inputting into Dave Thoma's Water Balance model (see 'Daily_WB_batch_v2.R'). The create_site_maps.R script creates a suite of maps from which the project lead can select the most appropriate for use with the RSS Powerpoint presentation. Maps output into the './figures/maps' folder. 

```{r Water-Balance, message=FALSE, warning=FALSE, echo = FALSE, results=HIDE}

source(here::here("scripts", "WaterBalance", "get_params.R")) # Extract site parameters

source(here::here("scripts", "Misc", "create_site_maps.R")) # Create site maps. If you cannot install Java, comment this line out. 
```

```{r}

if (exists("WB_GCMs") == FALSE) stop("Please specify GCMs for Water Balance")

source(here::here("scripts", "WaterBalance", "Daily_WB_batch_v2.R")) # Run the Water Balance Model

```


# Summary Plots

```{r Summary-Plots, message=FALSE, warning=FALSE, echo = FALSE, results=HIDE}

source(here::here("scripts", "SummaryPlots", "Summary plots.R"))

source(here::here("scripts", "SummaryPlots", "Summary WB plots.R")) 
```

# Additional Tables and Plots

```{r Additional-plots-and-tables, message= FALSE, warning=FALSE, echo=FALSE, results=HIDE}

source(here::here("scripts", "Additional-tables-plots", "RSS_MACA_drought_char.R"))

source(here::here("scripts", "Additional-tables-plots", "FLI FBI phenology plots.R"))

source(here::here("scripts", "Additional-tables-plots", "RSS Audubon summary.R"))
```
# Create metadata and copy/delete files

```{r Copy-and-delete-files, message=FALSE, warning=FALSE}

# This script is for copying and pasting files and folders unique to an RSS to a local folder, for the purposes of using, sharing, or archiving products. Files are then deleted from the Climate_Futures repo so that files are not inadvertently overwritten or confused with products from a different site.

source(here::here("scripts", "Misc", "write_metadata.R"))

source(here::here("scripts", "Misc", "copy_paste_delete_files.R")) # copies files and folders to specified local folder


```



