---
title: "Combine-climate-lite-scripts"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
abstract: This script combines all scripts previously run under CCRP's Climate Lite protocol for Resource Stewardship Strategies (RSS). 
---

```{r user-inputs}

rm(list = ls())

# -------------- Input site information -------------------------------------- #

SiteID = "CARE"
site <- "CARE" # This is entered twice because the object is assigned differently in different scripts. The park code will only be entered once in future versions. 
state <- "Utah"

# --------------- Input local folder information ----------------------------- #

# When this document has finished running, the files will be copied to a local directory and all newly created files (e.g., figures) will be deleted from the repo

project_root_dir <- 'C:/Users/msears/Documents/Repos/CCRP_Climate_Futures_v1.0' # local directory where your repo is stored
local_rss_dir <- 'C:/Users/msears/Documents/RSS/CARE/' # local directory where you want this repo copied. Should be something like 'C:/Users/adillon/Documents/RSS/CONG'

# -------------- Input information for Climate Futures analyses (MACA) ------- #

# Specify Climate Futures and Models

FutureSubset <- c("Warm Wet","Hot Dry") # Pick pair of climate futures.
CFs<- c("Warm Wet", "Hot Dry") # Same as above
colors2<- c("#9A9EE5","#E10720")  # Select pair of climate futures - WarmWet/HotDry
#colors2<- c("#F3D3CB","#12045C")  # Select pair of climate futures - HotWet/WarmDry
CFs_all <- c("Warm Wet", "Hot Wet", "Central", "Warm Dry", "Hot Dry")

# Specify parameters:

Year = 2040 #Central year
Range = 30  #Number of years to summarize (should be at least 30)

# Threshold percentages for defining Climate futures. Default low/high:  0.25, 0.75
CFLow = 0.25     
CFHigh = 0.75

#Temperature/precip threshold values

HotTemp = 95    # deg F. Default should be about 100 deg F
ColdTemp = 32    # deg F
PrecipThreshold = 0.05    # inches per day. Precip Threshold (used to measure Drought duration). For many GCMs shoud not 
#  be 0 because models "drizzle". Some investigation necessary.
QuantileLow = 0.05   #Quantiles for temperature threshold calculations
QuantileHigh = 0.95

# -------------- Input information for Water Balance model ------------------- #

WB_GCMs = c("CSIRO-Mk3-6-0.rcp45","HadGEM2-ES365.rcp85") # Specific models need to be selected to run the Water Balance scripts

col<- c("darkgray","#9A9EE5","#E10720")  # WarmWet/HotDry
#col<- c("darkgray","#F3D3CB","#12045C")  # HotWet/WarmDry

# The following files are inputs into this script. Change as necessary. 
inputs <- c(paste0(site, "_lat_long_PRISM_PptTminTmax_IntermediateFiles.RData"), 
            paste0(site, "_init_parsed.RData"), 
            "GridMet.csv")

# The following needs to be inputted if the park centroid will not be used to select the MACA grid cell for the water balance model:

#MACA_lat <- 40.4465 
#MACA_lon <- -108.7651

# ------------ Input information for Drought analyses ------------------------ #

## SPEI variables
SPEI_per<-6 # This is the value for the period SPEI is aggregated. 6-months is standard but could change if want. 
truncation<- -.5 # SPEI value, under which drought events are considered


```


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  collapse = TRUE,
  warning = TRUE, # set to FALSE when done
  message = TRUE # set to FALSE when done
)

#packrat::init(options = list(local.repos = c('./local-repos/WaterBalance'))) # Please do not run this line without consulting Amber Runyon or Annie Kellner

library(here); library(plyr); # Use here::here when package lubridate is used
library(plotrix); library(zoo); library(ggplot2); library(grid); library(cowplot); library(reshape2); library(raster); library(ncdf4); library(reshape2); library(WriteXLS); library(data.table); library(RColorBrewer); library(ggrepel);library(plyr); library(lubridate); library(dplyr); library(forcats); library(openxlsx); library("WaterBalance"); library(sf); library(raster); library(rgdal); library(R.utils); library(tmap); library(tmaptools); library(rJava); library(OpenStreetMap); library(gridExtra); library(SPEI); library(tidyr); library(tibble); library(sp); library(skimr) #library(cft)


```


## Historical Trends

```{r PRISM-parse, eval = FALSE, message=FALSE, warning=FALSE, echo=FALSE}

#source(here::here("./PRISM/PRISM_4k_parse.R")) # Parses PRISM data. Output = "PARK_lat_long_PRISM_PptTminTmax_IntermediateFiles.RData" # NOTE: This script is excluded and has not been adapted to the new process

```

```{r Historical-trends-plots, results=hide, eval=TRUE} 

# Requires "PARK_lat_long_PRISM_PptTminTmax_IntermediateFiles.RData"
# Outputs plots into ./figures/Historical-trends

source(here::here("scripts", "Historical-trends", "RSS PRISM plots v1.2.R"),echo = FALSE) 

```


## Climate Futures (MACA)

```{r Climate-Futures, echo=FALSE, message=FALSE, warning=FALSE, results=HIDE}

# source(here::here("RSS_MACA_Parsing.R")) # Parse MACA data. Output = "_init_parsed.RData". 
# source(here::here("Gridmet-Parse.R")) # Parse GridMET data. Output = "GridMet.csv"

source(here::here("scripts", "Climate-Futures", "RSS_MACA_Plot_Table_Creation.R"), local = knitr::knit_global()) # Requires "PARK_init_parsed.RData"; Output = "PARK_lat_long_Final_Environment.RData". 

source(here::here("scripts", "Climate-Futures", "RSS_MACA_Scatter and diagnostic.R"), local = knitr::knit_global()) # Creates scatter and diagnostic plots. Outputs to Figs MACA folder. 
```

```{r CF-plots}

if (exists("FutureSubset") == FALSE) stop("Please specify Climate Futures") # At the top of the script, please enter a combination of futures, e.g. Warm Wet/Hot Dry

source(here::here("scripts", "Climate-Futures", "RSS_Plotting_Bar_Charts.R")) # Requires "PARK_lat_long_Final_Environment.RData". Outputs plots and Excel Workbook 

```

# Water Balance

The get_params.R script extracts site parameters for inputting into Dave Thoma's Water Balance model (see 'Daily_WB_batch_v2.R'). The create_site_maps.R script creates a suite of maps from which the project lead can select the most appropriate for use with the RSS Powerpoint presentation. Maps output into the './figures/maps' folder. 

```{r Water-Balance, message=FALSE, warning=FALSE, echo = FALSE, results=HIDE}

source(here::here("scripts", "WaterBalance", "get_params.R")) # Extract site parameters

source(here::here("scripts", "Misc", "create_site_maps.R")) # Create site maps
```

```{r}

if (exists("GCMs") == FALSE) stop("Please specify GCMs")

source(here::here("scripts", "WaterBalance", "Daily_WB_batch_v2.R")) # Run the Water Balance Model

```


# Summary Plots

```{r Summary-Plots, message=FALSE, warning=FALSE, echo = FALSE, results=HIDE}

source(here::here("scripts", "SummaryPlots", "Summary plots.R"))

source(here::here("scripts", "SummaryPlots", "Summary WB plots.R")) 
```

# Additional Tables and Plots

```{r Additional-plots-and-tables, message= FALSE, warning=FALSE, echo=FALSE, results=HIDE}

source(here::here("scripts", "Additional-tables-plots", "RSS_MACA_drought_char.R"))

source(here::here("scripts", "Additional-tables-plots", "FLI FBI phenology plots.R"))

source(here::here("scripts", "Additional-tables-plots", "RSS Audubon summary.R"))
```

```{r Testing, eval = FALSE}

# Final Environment created in this script

file <- list.files(path = './data/park-specific/output', pattern = 'Final_Environment.RData', full.names = TRUE) 
load(file)

final_new <- rbind(H_annual, F_annual)

summary_new <- final_new %>%
  group_by(CF) %>%
  skim() %>%
  yank("numeric") %>%
  select(-c(n_missing, complete_rate, hist))

# Final Environment created using old system

old <- list.files(path = './data/park-specific/old', pattern = 'Final_Environment.RData', full.names = TRUE)
load(old)

final_old <- rbind(H_annual, F_annual)
final_old <- final_old %>% select(-Sp.Frost)

summary_old <- final_old %>%
  group_by(CF) %>%
  skim() %>%
  yank("numeric") %>%
  select(-c(n_missing, complete_rate, hist))

# Compare

diff <- summary_new %>%
  dplyr::select(skim_variable, CF)

diff[,3] <- summary_new[,3] - summary_old[,3]
diff[,4] <- summary_new[,4] - summary_old[,4]
diff[,5] <- summary_new[,5] - summary_old[,5]
diff[,6] <- summary_new[,6] - summary_old[,6]
diff[,7] <- summary_new[,7] - summary_old[,7]
diff[,8] <- summary_new[,8] - summary_old[,8]
diff[,9] <- summary_new[,9] - summary_old[,9]

diff
  
```


```{r Copy-and-delete-files, message=FALSE, warning=FALSE}

# This script is for copying and pasting files and folders unique to an RSS to a local folder, for the purposes of using, sharing, or archiving products. Files are then deleted from the Climate_Futures repo so that files are not inadvertently overwritten or confused with products from a different site.

source(here::here("scripts", "Misc", "copy_paste_delete_files.R")) # copies files and folders to specified local folder


```



