---
title: "Combine-climate-lite-scripts"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
abstract: This script combines all scripts previously run under CCRP's Climate Lite protocol for Resource Stewardship Strategies (RSS). 
---

```{r user-input}

rm(list = ls())

SiteID = "CONG"
site <- "CONG"
state <- "South Carolina"


# When this document has finished running, the files will be copied to a local directory and all newly created files (e.g., figures) will be deleted from the repo

project_root_dir <- 'C:/Users/adillon/Documents/Repos/CCRP_Climate_Futures_dev' # local directory where your repo is stored
local_rss_dir <- 'C:/Users/adillon/Documents/RSS/CONG/Test' # local directory where you want this repo copied. Should be something like 'C:/Users/adillon/Documents/RSS/CONG'

# Input Climate Futures

FutureSubset <- c("Warm Wet","Hot Dry") # Pick pair of climate futures.

# The following needs to be inputted if the park centroid will not be used to select the MACA grid cell for the water balance model:

#MACA_lat <- 40.4465 
#MACA_lon <- -108.7651

```



```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  collapse = TRUE,
  warning = TRUE, # set to FALSE when done
  message = TRUE # set to FALSE when done
)

#packrat::init(options = list(local.repos = c('./local-repos/WaterBalance'))) # This should only have to be entered once

library(here); library(plyr); # Use here::here when package lubridate is used
library(plotrix); library(zoo); library(ggplot2); library(grid); library(cowplot); library(reshape2); library(raster); library(ncdf4); library(reshape2); library(WriteXLS); library(data.table); library(RColorBrewer); library(ggrepel);library(plyr); library(lubridate); library(dplyr); library(forcats); library(openxlsx); library("WaterBalance"); library(sf); library(raster); library(rgdal); library(R.utils); library(tmap); library(tmaptools); library(rJava); library(OpenStreetMap); library(gridExtra); library(SPEI); library(tidyr); library(tibble); library(sp); #library(cft)


```


## Historical Trends (PRISM)

```{r PRISM-parse, eval = FALSE, message=FALSE, warning=FALSE, echo=FALSE}

#source(here::here("./PRISM/RSS PRISM AN81 4km summarize v01.1.R")) # Parses PRISM data. Output = "PARK_lat_long_PRISM_PptTminTmax_IntermediateFiles.RData" # NOTE: Because this script is excluded, headers have not been changed

```

```{r PRISM-plots, results=hide, eval=TRUE} 

source(here::here("scripts", "PRISM", "RSS PRISM plots v1.2.R"),echo = FALSE)

```


## Climate Futures (MACA)

```{r Climate-Futures, echo=FALSE, message=FALSE, warning=FALSE, results=HIDE}

# source(here::here("RSS_MACA_Parsing.R")) # Parse MACA data. Output = "_init_parsed.RData". Outputs to MACA folder.

# source(here::here("Gridmet-Parse.R")) # Parse GridMET data. Output = "GridMet.csv". Outputs to Gridmet folder.

source(here::here("scripts", "Climate-Futures", "RSS_MACA_Plot_Table_Creation.R"), local = knitr::knit_global()) # Requires "PARK_init_parsed.RData"; Output = "PARK_lat_long_Final_Environment.RData". 

source(here::here("scripts", "Climate-Futures", "RSS_MACA_Scatter and diagnostic.R"), local = knitr::knit_global()) # Creates scatter and diagnostic plots. Outputs to Figs MACA folder. 
```

```{r Input-Climate-Futures}

if (exists("FutureSubset") == FALSE) stop("Please specify Climate Futures")

source(here::here("scripts", "Climate-Futures", "RSS_Plotting_Bar_Charts.R")) # Requires "PARK_lat_long_Final_Environment.RData". Outputs plots and Excel Workbook to Figs MACA folder.

```




```

# Water Balance

```{r Water-Balance, message=FALSE, warning=FALSE, echo = FALSE, results=HIDE}

source(here::here("scripts", "WaterBalance", "get_params.R"))

source(here::here("scripts", "WaterBalance", "Daily_WB_batch_v2.R")) 
```

# Summary Plots

```{r Summary-Plots, message=FALSE, warning=FALSE, echo = FALSE, results=HIDE}

source(here::here("scripts", "SummaryPlots", "Summary plots.R"))

source(here::here("scripts", "SummaryPlots", "Summary WB plots.R")) 
```

# Additional Tables and Plots

```{r Additional-plots-and-tables, message= FALSE, warning=FALSE, echo=FALSE, results=HIDE}

source(here::here("scripts", "Additional-tables-plots", "RSS_MACA_drought_char.R"))

source(here::here("scripts", "Additional-tables-plots", "FLI FBI phenology plots.R"))

source(here::here("scripts", "Additional-tables-plots", "RSS Audubon summary.R"))
```

```{r Testing}

# Final Environment created in this script

file <- list.files(path = './data/RData', pattern = 'Final_Environment.RData', full.names = TRUE) 
load(file)

final_new <- rbind(H_annual, F_annual)

summary_new <- final_new %>%
  group_by(CF) %>%
  skim() %>%
  yank("numeric") %>%
  select(-c(n_missing, complete_rate, hist))

# Final Environment created using old system

old <- list.files(path = './data/RData/old', pattern = 'Final_Environment.RData', full.names = TRUE)
load(old)

final_old <- rbind(H_annual, F_annual)

summary_old <- final_old %>%
  group_by(CF) %>%
  skim() %>%
  yank("numeric") %>%
  select(-c(n_missing, complete_rate, hist))

# Compare

diff <- summary_new %>%
  dplyr::select(skim_variable, CF)

diff[,3] <- summary_new[,3] - summary_old[,3]
diff[,4] <- summary_new[,4] - summary_old[,4]
diff[,5] <- summary_new[,5] - summary_old[,5]
diff[,6] <- summary_new[,6] - summary_old[,6]
diff[,7] <- summary_new[,7] - summary_old[,7]
diff[,8] <- summary_new[,8] - summary_old[,8]
diff[,9] <- summary_new[,9] - summary_old[,9]

diff
  

```


```{r Copy-and-delete-files, message=FALSE, warning=FALSE}

# Create folder structure locally

# Scripts

scripts_local_dir = paste(local_rss_dir, "scripts", sep = '/')
if(dir.exists(scripts_local_dir) == FALSE){
  dir.create(scripts_local_dir)
}

scripts_repo_dir <- paste(project_root_dir, "scripts", sep = '/')

copyDirectory(from = scripts_repo_dir, to = scripts_local_dir, recursive = TRUE)

# Figures

figs_local_dir = paste(local_rss_dir, "figures", sep = '/')
if(dir.exists(figs_local_dir) == FALSE){
  dir.create(figs_local_dir)
}

figs_repo_dir <- paste(project_root_dir, "figures", sep = '/')

copyDirectory(from = figs_repo_dir, to = figs_local_dir, recursive = TRUE)

# Data

data_local_dir = paste(local_rss_dir, "data", sep = '/')
if(dir.exists(data_local_dir) == FALSE){
  dir.create(data_local_dir)
}

data_repo_dir <- paste(project_root_dir, "data", sep = '/')

copyDirectory(from = data_repo_dir, to = data_local_dir, recursive = TRUE)

# Remove spatial files

spatial_dir <- paste(data_local_dir, "spatial-data", sep = "/")
unlink(spatial_dir, recursive = TRUE)

# Rmd file

rmd <- list.files(project_root_dir, pattern = '.Rmd') 
file.copy(file.path(project_root_dir, rmd), local_rss_dir)

# Remove figures and derived data from repo

deriv_data <- paste(data_repo_dir, "derived-data", sep = '/')

unlink(deriv_data, recursive = TRUE)
unlink(figs_repo_dir, recursive = TRUE)

```



